\phSection{Leagues}

Each team is registered in either the \textbf{Competitive or Recreational League}.
If both Leagues are playing simultaneously today at your campus, then all
scoring and awards are handled separately in both Leagues.

\phSection{Puzzle Packets and ClueKeeper}

Each team has received multiple \textbf{Puzzle Packets}. However, there is
not enough information in this packet to begin solving any puzzles.

Once the game begins, clues will become available in the \textbf{ClueKeeper} app that
will allow players to begin solving puzzles in the packet. Once a puzzle is
solved, its solution can be submitted via the app. As time progresses, hints
for unsolved puzzles will unlock, helping teams who are stuck. The game
ends when your time in ClueKeeper has expired.

\phSection{Main Puzzles}

Once the game begins, you'll be presented with four \textbf{Main Puzzles}. 
Each Main Puzzle can be solved directly using mathematical modeling
and problem-solving abilities. Once the solution for the puzzle has been
entered into ClueKeeper, \textbf{1000 Victory Points} will be awarded,
and the second part will be unlocked. This second part uses the first
solution to extract a short word or phrase. Solving this second challenge
is worth an additional \textbf{500 Victory Points}.

\phSection{Cryptic Puzzles}

After solving the second part of each Main Puzzle, an additional
\textbf{Cryptic Puzzle} will become available to solve.
The way to solve these puzzles is left, well,
cryptic. However, your team should still be able to use your
critical thinking to extract a hidden word or phrase. Correct
solutions are worth \textbf{500 Victory Points}.

\phSection{Bonus Puzzle}

After solving all four Main Puzzles, the Bonus Puzzle will become unlocked
in ClueKeeper. Your team will be asked to optimize a certain task, and
present your solution to Game Control in person, which will be graded and
awarded \textbf{up to 500 Victory Points}. 

You may submit up to three solutions throughout
the game (including any disqualified submissions), and your best solution of the
three will be counted toward your score. You must bring a device with the 
ClueKeeper app with you to submit an answer; as long as your time has not
expired when you arrive at Game Control, you will be able to submit your
answer (even if you have to wait on other teams ahead of you first).

\phSection{Metapuzzle}

Once your team has solved two Cryptic Puzzles, the final \textbf{Metapuzzle}
becomes available, worth \textbf{1000 Victory Points}.

\newpage

\phSection{Hints}

Recreational teams may ask for hints at Game Control at any time during
the game, and may receive direct assistance from their teachers/chaperones
as desired.
Competitive teams may ask Game Control for rules clarifications or help
with the ClueKeeper app (including help with entering solutions
for the first part of a Main Puzzle), but otherwise
will only receive help via hints made available in ClueKeeper.

\phSection{Winning the Game}

The team that earns the \textbf{most Victory Points out of 10000}
by the end of the game is the \textbf{winner}, with ties broken based
on which team solved their final non-Bonus puzzle earliest. 

\phSection{Additional Rules/Advice}

\begin{itemize}
\item Players should not do anything which
would interfere with other teams solving puzzles. Be a good sport!
\item Submissions for each puzzle, besides the Bonus Puzzle, are unlimited.
Every submission for the Bonus Puzzle will be carefully graded by Game Control,
so only three submissions are allowed.
\item Before visiting Game Control to ask for a hint or clarification, make
sure you've read all the material accompanying the puzzle! Chances are,
your question is covered there.
\item Teachers and chaperones are not allowed to help Competitive teams solve
puzzles.
\item Teams may use any supplies they've brought and even
look things up online to solve puzzles, but Competitive Teams may not receive any direct
assistance from outside their team (e.g. you can't Phone a Friend).
\item Players must remain within any physical boundaries set by both
Game Control and their teacher/chaperone at all times, and must always
travel with a teammate when leaving their headquarters.
\item Teachers/chaperones are responsible for their students at
all times.
\item Since this game will be played at different campuses on different
days, please do not spoil any of today's puzzles or solutions online until
the game book is released publicly by MaPP!
\item Contact Game Control immediately in the case of emergency
or any issues with these rules.
\end{itemize}

