The Cosmic Wheel is one of the major shipping hubs of the galaxy...
at least it was before it was hit by a violent Tachyon storm,
breaking down the Cosmic Wheel's five 
\textbf{Wormholes: Alpha, Beta, Gamma, Omega,} and \textbf{Zeta}! 
These wrinkles in space-time have been
unfolded by the Tachyon storm, mixing each wormhole's 
\textit{light gray entrances} and \textit{dark gray exits}
with unshaded empty space.

Fortunately, your team may be able to lend a hand
by remotely manipulating space-time as easily as folding
a regular piece of paper! Here's how this amazing technology
works.

\begin{enumerate}
  \item Cut out the \(12\times12\) square from each Wormhole page.
  \item You may fold the paper along any line (vertical, horizontal, or diagonal), 
  but you are not allowed to tear the paper.
  (Ripping apart space-time is incredibly dangerous!)
  \item Each paper should be folded into a smaller square of the size
  designated on the page: either
  \(4\times4\), \(5\times5\), or \(6\times6\). 
  \item Your goal is to repair each wormhole as completely as possible. 
  A repaired wormhole is completely light gray on one side (its entrance) 
  and completely dark gray on the other (its exit).
\end{enumerate}

Can your team repair all five wormholes?
No pressure, it's just the jobs of 9 trillion hard-working Geeftus traders
(not to mention their spouses and an average of 7 children each) on the line!

\textbf{SCORING}

This puzzle should be submitted in person to Game Control, who will award up to
500 Victory Points based on the quality of your submission.
Your team is allowed up to three submissions (including disqualified
submissions); the best score of these will be counted toward your overall
total for the game. Review the following criteria 
carefully to optimize your score (and avoid a disqualified submission)!

\begin{itemize}
  \item You must submit exactly one folded copy of each of the 
    five wormholes in the appropriate dimension.
  \item The paper may only be folded along the given vertical,
    horizontal, or diagonal lines.
  \item The back side of the paper must not be visible.
  \item When submitting, your team must choose which side of each 
    folded wormhole serves as the entrance (light gray),
    and the other side will serve as the exit (dark gray).
  \item Each entrance will be scored by the percentage area that
    is light gray minus the percentage area that is dark gray.
    (Unshaded area doesn't count for or against.)
  \item Each exit will be scored by the percentage area that
    is dark gray minus the percentage area that is light gray.
    (Unshaded area doesn't count for or against.)
  \item These ten percentages will be summed together and divided 
    by two to calculate your Bonus Puzzle score out of 500, 
    rounded down to the nearest integer as needed.
\end{itemize}
